Neighbor-Based Decentralized Training Strategies for Multi-Agent Reinforcement Learning

### 2024-09-17 paper-2024-sac-marl-neighbouring-strategies.tex
chore: on paper
chore: add details

\author{Ben Trovato}
\authornote{Dr.~Trovato insisted his name be first.}
\orcid{1234-5678-9012}
\affiliation{%
  \institution{Institute for Clarity in Documentation}
  \streetaddress{P.O. Box 1212}
  \city{Dublin} 
  \state{Ohio} 
  \country{USA}
  \postcode{43017-6221}  
}
\email{trovato@corporation.com}

\author{G.K.M. Tobin}
\authornote{The secretary disavows any knowledge of this author's actions.}
\affiliation{%
  \institution{Institute for Clarity in Documentation}
  \streetaddress{P.O. Box 1212}
  \city{Dublin} 
  \state{Ohio} 
  \country{USA}
  \postcode{43017-6221}  
}
\email{webmaster@marysville-ohio.com}

\author{Lars Th{\o}rv{\"a}ld}
\authornote{This author is the
  one who did all the really hard work.}
\affiliation{%
  \institution{The Th{\o}rv{\"a}ld Group}
  \streetaddress{1 Th{\o}rv{\"a}ld Circle}
  \city{Hekla} 
  \country{Iceland}}
\email{larst@affiliation.org}

\author{Valerie B\'eranger}
\affiliation{%
  \institution{Inria Paris-Rocquencourt}
  \city{Rocquencourt}
  \country{France}
}
\author{Aparna Patel} 
\affiliation{%
 \institution{Rajiv Gandhi University}
 \streetaddress{Rono-Hills}
 \city{Doimukh} 
 \state{Arunachal Pradesh}
 \country{India}}
\author{Huifen Chan}
\affiliation{%
  \institution{Tsinghua University}
  \streetaddress{30 Shuangqing Rd}
  \city{Haidian Qu} 
  \state{Beijing Shi}
  \country{China}
}

\author{Charles Palmer}
\affiliation{%
  \institution{Palmer Research Laboratories}
  \streetaddress{8600 Datapoint Drive}
  \city{San Antonio}
  \state{Texas} 
  \country{USA}
  \postcode{78229}}  
\email{cpalmer@prl.com}

% The default list of authors is too long for headers}
\renewcommand{\shortauthors}{B. Trovato et al.}

\begin{abstract}
  Multi-Agent Reinforcement Learning (MARL) is gaining popularity as a powerful framework for training agents to collaborate and compete in complex environments. However, MARL introduces unique challenges, such as non-stationarity and partial observability, that complicate the training process.  
  While centralized training methods can address some of these challenges, they often face scalability limitations as the number of agents grows. This paper investigates the effectiveness of various neighbor-based decentralized training strategies as a viable alternative to centralized training. We evaluate Experience Sharing, Nearest Neighboring Averaging, and Nearest Neighboring Consensus methods in a custom multi-agent environment and compare their performance against centralized training. Our results show that neighbor-based methods can achieve comparable performance to centralized training while offering improved scalability and communication efficiency. 
  We discuss the trade-offs between these methods and provide insights into their applicability in different scenarios.
  %% More -- add the fact that this make it possible to train agents in a decentralized manner, which is more realistic and scalable than centralized training.
\end{abstract}
%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>  
\end{CCSXML}

@@

\keywords{ACM proceedings, \LaTeX, text tagging}
\maketitle

@@

\bibliographystyle{ACM-Reference-Format}
\bibliography{sample-bibliography}

>>>>

\author{Nicolò Malucelli}
\orcid{1234-5678-9012}
\affiliation{%
  \institution{University of Bologna}
  \streetaddress{Via dell'Università, 50}
  \city{Cesena} 
  \country{Italy}
}
\email{nicolò.malucelli@studio.unibo.it}

\author{Davide Domini}
\orcid{1234-5678-9012}
\affiliation{%
  \institution{University of Bologna}
  \streetaddress{Via dell'Università, 50}
  \city{Cesena} 
  \country{Italy}
}
\email{davide.domini@unibo.it}

\author{Gianluca Aguzzi}
\affiliation{%
  \institution{University of Bologna}
  \streetaddress{Via dell'Università, 50}
  \city{Cesena} 
  \country{Italy}
}
\email{gianluca.aguzzi@unibo.it}

\author{Mirko Viroli}
\affiliation{%
  \institution{University of Bologna}
  \streetaddress{Via dell'Università, 50}
  \city{Cesena} 
  \country{Italy}
}
\email{mirko.viroli@unibo.it}

% The default list of authors is too long for headers}
\renewcommand{\shortauthors}{N. Malucelli et al.}

\begin{abstract}
  Multi-Agent Reinforcement Learning (MARL) is gaining popularity as a powerful framework for training agents to collaborate and compete in complex environments. However, MARL introduces unique challenges, such as non-stationarity and partial observability, that complicate the training process.  
  While centralized training methods can address some of these challenges, they often face scalability limitations as the number of agents grows. This paper investigates the effectiveness of various neighbor-based decentralized training strategies as a viable alternative to centralized training. We evaluate Experience Sharing, Nearest Neighboring Averaging, and Nearest Neighboring Consensus methods in a custom multi-agent environment and compare their performance against centralized training. Our results show that neighbor-based methods can achieve comparable performance to centralized training while offering improved scalability and communication efficiency. 
  We discuss the trade-offs between these methods and provide insights into their applicability in different scenarios.
  %% More -- add the fact that this make it possible to train agents in a decentralized manner, which is more realistic and scalable than centralized training.
\end{abstract}
%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>  
\end{CCSXML}

@@

\keywords{Multi-Agent Reinforcement Learning, Decentralized Training, Neighbor-Based Methods, Scalability, Communication Efficiency}
\maketitle

@@

\bibliographystyle{ACM-Reference-Format}
\bibliography{bibliography}
